\documentclass[11pt]{amsart}
\usepackage[margin = 1.25in]{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{microtype}
\usepackage{listings}
\usepackage{color}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}




\title{User Documentation}
\author{Group N: Femi, David, Eric, Kenneth, Evan}
%\date{}                                           % Activate to display a given date or no date

\begin{document}
\maketitle
\section{Introduction}
\noindent The goal of this project is to replicate a paper document used to apply for Teaching Assistant positions in an electronic format. Using this product, a student can apply for positions (TA if graduate student, PLA if undergraduate) in a specific class of their choosing in the Computer Science Department. The application will be accessible online through a browser, and will, at least partly, automate the process of sorting through applicants for the instructor.
%\subsection{}
\section{Users}


\subsection{All Users}

\begin{itemize}
	\item{Sign into an account}
	\begin{itemize}
		\item{Go to \href{http://applyta-teamnovember.rhcloud.com/}{http://applyta-teamnovember.rhcloud.com/}}
		\item{Enter your credentials, and then click sign in}
	\end{itemize}
	\item{Sign out of an account}
	\begin{itemize}
		\item{On the left side menu on any page, click the Sign Out button at the bottom}
	\end{itemize}
\end{itemize}

\subsection{Applicants}

\begin{itemize}
	\item{Apply to become a TA/PLA}
	\begin{itemize}
		\item{On the left side menu on any page, click the Apply button}
		\item{Fill out each field and page of the form with accurate data}
		\item{When you reach the final page, hit the Submit button at the bottom right of the screen to submit your application}
	\end{itemize}
	\item{Override a current submission?}
	\begin{itemize}
		\item{}
		\item{}
	\end{itemize}
	\item{View personal submission and status of submission?}
	\begin{itemize}
		\item{}
		\item{}
	\end{itemize}
\end{itemize}

\subsection{Professors}

\begin{itemize}
	\item{View accepted and relevant applicants}
	\begin{itemize}
		\item{Log in, or, on the left side menu on any page, click the Home button.}
	\end{itemize}
	\item{View/Download? resumes from applicants?}
	\begin{itemize}
		\item{}
		\item{}
	\end{itemize}
	\item{View and Create comments on an applicant}
	\begin{itemize}
		\item{While viewing applicants, click the View/Add button for any applicant}
		\item{While viewing the applicant, enter text into the Comments text box and then click the Add Comment button to add a comment}
	\end{itemize}
	\item{View taught courses}
	\begin{itemize}
		\item{While viewing applicants, click the View Courses button at the top of the page}
		\item{Select the course you wish to view by clicking the View Applicants button}
	\end{itemize}
	\item{Add/remove applicants from a shopping cart}
	\begin{itemize}
		\item{While viewing applicants, click the + - Button to add a student not in the course's shopping cart, or to remove a student in the course's shopping cart.}
		\item{While viewing a course, click the button to remove the applicant from the course's shopping cart}
	\end{itemize}
\end{itemize}

\subsection{Graduate Program Director?}

\begin{itemize}
	\item{View all applicants}
	\begin{itemize}
		\item{After logging in, applicants who are not yet approved or unapproved show in the top table}
		\item{applicants who are approved show in the table under the first table}
		\item{applicants who are unapproved show in the bottom table}
	\end{itemize}
	\item{Accept or deny applicants}
	\begin{itemize}
		\item{In the first and last tables, for any student, click the Accept button to accept the application into the system}
		\item{In the first and second table, for any student, click the Not Accepted/Deny button to indicate that the application is not accepted into the system}
	\end{itemize}
\end{itemize}

\subsection{Administrators}

\begin{itemize}
	\item{View all unaggisned and assigned applicants}
	\begin{itemize}
		\item{Log in, then scroll below the admin panel}
	\end{itemize}
	\item{Assign a TA/PLA to a class}
	\begin{itemize}
		\item{For any applicant in the tables, click the dropdown and select a course to assign them to, then click the select button.}
	\end{itemize}
	\item{Add a course}
	\begin{itemize}
		\item{In the Admin Panel, enter the course name to be entered into the course name field, and then select a professor from the dropdown. Click the add button to add the course}
	\end{itemize}
	\item{Remove a course}
	\begin{itemize}
		\item{In the Admin Panel, Select a course from the Remove Courses dropdown, and then click the Remove button in order to remove it.}
	\end{itemize}
	\item{Set temporal windows}
	\begin{itemize}
		\item{In the Admin Panel, enter dates into the forms at the bottom to set the temporal windows as indicated}
	\end{itemize}
\end{itemize}


\end{document}  